\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-15 chapters/0_abstract.tex
Update supplementaries

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints, i.e. mutual exclusion between clusters. These different combinations then correspond to existing clustering methods as well as new algorithms that we introduce and analyze. We evaluate these different algorithms on instance segmentation, which is the task of partitioning an image into distinct segments, by predicting edge weights with a CNN. \UPDATE{Summarize results} 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
\today,\currenttime - 
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints, i.e. mutual exclusion between clusters. These different combinations then correspond to existing clustering methods as well as new algorithms that we introduce and analyze. We evaluate these different algorithms on instance segmentation, which is the task of partitioning an image into distinct segments, by predicting edge weights with a CNN. \UPDATE{Summarize results} 
\end{abstract}

### 2019-05-15 chapters/3_algorithm.tex
Update supplementaries

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        \EndIf
        % \State
        \If{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

>>>>

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{\algname{}: Generalized Algorithm for Signed Graph Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}\texttt{addCannotLinkConstraints}}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ with each node in its own cluster
      \State Initial interactions between nodes given by $\cost_e = w^+_e - w^-_e$
      % \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      % \State Sort edges in priority queue (PQ) in descending order of absolute weight $|\cost_e|=|w^+_e - w^-_e|$ 
      % \State
      \Repeat
        \State Select pair of clusters $S_u,S_v\in\Pi$ with highest absolute interaction $|\interact{}(S_u,S_v)|$
        % \State
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ are \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$: update interactions and cannot-link constraints with all their neighbors
        % \State
        \ElsIf{\big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big] \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State Add CannotLink Constraint between clusters $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \big[all adjacent clusters are constrained\big]}
        % \If{({\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
        %   \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
        %     % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
        %     \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
        %   \EndFor
        % \EndIf
        % \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
        %   \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        % \EndIf

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data. Only the few wrongly segmented regions are highlighted in colors. Red arrows point to wrongly split regions. Yellow arrows point out merge errors. Green arrows indicate challenging, but correctly segmented regions. 
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

### 2019-05-15 chapters/5_experiments_compare_rules.tex
Update supplementaries

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge \cite{cremiChallenge} training data. Only the few wrongly segmented regions are highlighted in colors. Red arrows point to wrongly split regions. Yellow arrows point out merge errors. Green arrows indicate challenging, but correctly segmented regions. 
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}
\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand} & \makecell{VI-Merge} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
DTWS + LMC \cite{beier2016efficient}& -& & \\
DTWS + avgHC &-& & \\
DTWS  & -& & \\
THRESH &-& & \\ \hline
\algname{} & Average& 0.936 & 0.685 \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 & 0.642 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 & 0.714 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 & 0.539 \\
        \end{tabular}
    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{\UPDATE{TBD:} Scores on test data}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

>>>>

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \algname{} Linkage & \makecell{Arand-Score}  \\ \midrule \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC (LR)& -& 0.903 $\pm$ 0.016 \\
DTWS + MC (LR)& -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores and VI-Scores on CREMI challenge training data}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|c|c}
         & \makecell{CREMI \\Score} & \makecell{Arand\\Score} \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
PNI-UNet & 0.228 & 0.116 \\
Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
    \captionof{table}{\UPDATE{TBD:} Scores on test data}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}

### 2019-05-15 chapters/5_experiments_noise.tex
Update supplementaries

        \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
        \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data sample B, depending on the amount of noise (x-axis) added to the CNN predictions. \textbf{Top}: Accuracy given by Rand-Score (higher is better). Solid lines represent median values. Values between the 25th and the 75th percentile are shown in shade areas. \textbf{Bottom}: Multicut objective (Eq. \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value 1. \UPDATE{CLC}  
}\label{fig:noise_plots}
\end{figure}

@@

\subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
As shown in Table \ref{tab:results_cremi_train}, among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}. This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters, like LMC. 
In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of \algname{} and in Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all linkage tested with \algname{} on the full CREMI training data.

In order to highlight the properties and the strengths of each linkage criteria and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise. In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see visual example in Fig. \ref{fig:noisy_affs}).

>>>>

        \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
        \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{Performances of \algname{} with different linkage criteria on a crop of CREMI training data sample B, depending on the amount of noise (x-axis) added to the CNN predictions. \textbf{Top}: Accuracy given by Rand-Score (higher is better). Solid lines represent median values. Values between the 25th and the 75th percentile are shown in shade areas. \textbf{Bottom}: Multicut objective (Eq. \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero.
}\label{fig:noise_plots}
\end{figure}

@@

\subsection{Results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} \label{sec:comparison_exps}
As shown in Table \ref{tab:results_cremi_train}, among all the signed graph algorithms included in our generalized framework, the less-known one with \emph{Average} linkage consistently outperformed all other previously proposed linkage like \emph{Sum} or \emph{Absolute Max}. This method also achieved \UPDATE{comparable} scores to other complex multi-step pipelines that usually require the user to tune several hyper-parameters, like LMC. 
In Fig. \ref{fig:cremi_comparison}, we highlight some failure cases of \algname{} and in Appendix we provide an extended version of Table \ref{tab:results_cremi_train} including all linkage tested with \algname{} on the full CREMI training data.

In order to highlight the properties and the strengths of each linkage criteria and  perform an in-depth comparison that is as quantitative as possible, we run an additional set of experiments where we perturbed the CNN predictions with noise. In Appendix, we provide all the details about the used type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences (see example in Fig. \ref{fig:noisy_affs}).
